Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits

### 2018-11-07 Manuscript_draft/Manuscript_draft.Rmd
preparing files :)

---
title: Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits 
author:
- affilnum: '1,2'
  name: Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader
- affilnum: 3
  email: barragansljose@gmail.com
  name: null
affiliation:
- affil: US Environmental Protection Agency, Office of Research and Development, National
    Health and Environmental Effects Research Laboratory, Atlantic Ecology Division,
    27 Tarzwell Drive  Narragansett, RI, 02882, USA
  affilnum: 1
- affil: Big Name University, Department of R, City, BN, 01020, USA
  affilnum: 2
- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
  affilnum: 3
output:
  word_document: null
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    includes:
      in_header: header.tex
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
  html_document: null
capsize: normalsize
classoption: a4paper
csl: ecology.csl
documentclass: article
fontsize: 11pt
footerdate: yes
geometry: margin=1in
linenumbers: yes
bibliography:
- references.bib
- knitcitations.bib
spacing: doublespacing
abstract: no
---

@@

*Keywords*: heterospecific pollen, plant reproduction, fitness, competition

@@

@@

Discuss.

>>>>

---
title: Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits 
author:
- affilnum: '1,2'
  name: Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader
- affilnum: 3
  email: barragansljose@gmail.com
  name: Jose
affiliation:
- affil: US Environmental Protection Agency, Office of Research and Development, National
    Health and Environmental Effects Research Laboratory, Atlantic Ecology Division,
    27 Tarzwell Drive  Narragansett, RI, 02882, USA
  affilnum: 1
- affil: Big Name University, Department of R, City, BN, 01020, USA
  affilnum: 2
- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
  affilnum: 3
output:
  word_document: null
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    includes:
      in_header: header.tex
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
  html_document: null
capsize: normalsize
classoption: a4paper
csl: ecology.csl
documentclass: article
fontsize: 11pt
footerdate: yes
geometry: margin=1in
linenumbers: yes
bibliography:
- references.bib
- knitcitations.bib
spacing: doublespacing
abstract: no
---

@@

*Keywords*: heterospecific pollen, plant reproduction, fitness, pollen competition

@@

[comment starts]()
Glasshouse trial
•	Species selected and why – how you made them co-flower
•	Give details of sources and planting seeds, growth medium in pots, temperature and light details
•	Hand crosses and how you did them, how you measured seed set over time.
•	Analyses of data – standardization, means, matrices etc.

•	Analyses and technical difficulties: We calculated effect size by subtracting the mean of the cross pollinated seed set by the mean effect of the HP pollen (explain exactly what figures you used to calculate this) – check with liam about potentially using missing values analyses for the species we don’t have?

Check that the method is working well to prove that your crosses were close to 50% results in SI i.e not all mixes were 50/50% and we have now counted all the pollen to make this a quantitative variable. We also need to factor in the point that we have different total abundances of pollen across our treatments, irrespective of ratios. 
To what extent are differences in the ratios of pollen applied by hand across different plant families influenced by plant traits such as pollen size, morphology and stigma surface type?

Results – may need to include amount of pollen in models as random factor- prefill matrix with missing value analyse for the species you don’t have.  
Question 1: how do different pollination treatments (100% HP, 50% HP, self and cross ) impact HP pollen across different plant families? Even with 100% HP one (or more species?) still produced seed set.

Result Effect size of Seed set ~ phylogenetic distance relationship
We found that the variation ?/ mean effect size of seed set is positively related to phylogenetic distance.  This means the more unrelated the species are, the greater the negative impact of heterospecific pollen (give stats  effect size i.e. Procrustes, X = 0.35; P = 0.03)

Question 2 : what are the main traits impacting HP impacts? (compatibility system, pollen size, stigma surface, wet/dry stigma, length of style etc.

Effect size of seed set ~ floral traits/ reproductive plant traits
We found that the three best terms to explain the variation in seed set is pollen/ovule ratio, stigma width and style length (Stats effect size i.e. X = 0.39, P = 0.02).  
Need to provide correlation matrix for all traits just for 10 species
Show both ways to present this.
Which particular traits do you find significant effects for?
Show this and give stats.
Present plot for each trait and effect size

[comment finishes]()

@@

Discussion

1.	 What are the implications of the findings?
